---
title: "How to analyze data in AvInertia"
author: "Christina Harvey"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to analyze data in AvInertia}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Hi Christina! This is a large header

## This is a smaller header

### Keep adding "#" in the Rmd file to continually decrease header size if you'd like

You can write text as you'd like. Then to inject code, use "```" to enclose
blocks of code and also use "{r}" to specify that is is R code. Like this:

```{r setup}
library(AvInertia)
```

These code "chunks" should have names. The one above is named "setup".

Here's another example:

```{r plot_some_stuff, fig.height=5, fig.width=5}
plot(1:10)
```

In the above chunk, I named the chunk "plot_some_stuff" and specified the figure's
height and width (in inches, I think?)

Emojis work too: 🐢
(But probably not in the code block!)

Whenever you would like to see the output of this file, hit the "Knit" button
above. It will "knit" an html file that will either show up in the "Viewer" pane
inside RStudio or in your web browser (you can set this however you'd like)
